### 2020-04-09 Report/aws_325ghz_study.tex
A first versio of Sec 3.1.

@@

\subsection{Overview of the 183, 229 and 325\,GHz bands}
%
The simulations in this sction are based on five Fascod climate scenarios
(Sec.~\ref{sec:fascod}), and performed with a fixed sensor viewing angle of
25$^\circ$. No hydrometeors are included. For simpler interpretetation of the
results, the reflectivity is set to have no frequency variation, i.e.\ the same
value is applied for all bands. The reflective is varied between 0 and 0.5.

\subsubsection{Clear-sky brightness temperatures}
%
Figure~\ref{fig:tb:r00} shows brightness temperatures over the three bands, for
a reflectivity of 0 (i.e.\ a blackbody surface). The figure takes into account
that the 183\,GHz channels of AWS are of single-sideband character, while for
229 and 325\,GHz averages of upper and lower sidebands are shown, plotted as
a function from the centre frequency on the lower side.

\begin{figure}[p]
  \centering
  \includegraphics[width=0.75\textwidth]{fascod_tb_r000}
  \caption{Solid lines show brightness temperatures for the lower wing of the
    183.31\,GHz transition. Dashed lines represent double-sideband measurements
    around 325.15\,GHz, with the mean of upper and lower band shown on the low
    side. Dash-dotted lines represent double-sideband measurements around
    229.00\,GHz in the same manner, but only over the bandwidth of the
    potential channel. For all three bands, spectra for all five
    Fascod scenarios are included.}
  \label{fig:tb:r00}
\end{figure}
\begin{figure}[p]
  \centering
  \includegraphics[width=0.75\textwidth]{fascod_tb_r050}
  \caption{Same as figure above, but with a surface reflectivity of 0.5.}
  \label{fig:tb:r00}
\end{figure}

For 183 and 325\,GHz the brightness temperatures increase when moving away from
the centre frequency of the transition. The ``kinks'' in the spectra correspond
to ozone transitions, that are both more frequent and stronger in the 325\,GHz
range than in the 183\,GHz one. See Fig.~1 of \citet{eriksson:towar:20} for how
the ozone transitions are distribbuted between the lower and uper 325\,GHz sideband. 
The spectra of 183 and 325\,GHz deviate little close to the trasition
frequency, showing that the two frequencies are of similar strength, though the
325\,GHz one is slightly weaker. The higher deviation further out in the wings
is due to different contribution of far wing and continuum absorption. This
contribution is higher at 325\,GHz. The 229\,GHz brightness temperatures is
higher than any value around 183 and 325\,GHz, as expected 229\,GHz being a
window channel.

In Figure~\ref{fig:tb:r00} the surface reflectivity is changed to 0.5, which
should roughly correspond to the highest reflectivity encountered at these
frequencies. The differences between the two figures are small for 183 and
325\,GHz tor the tropical and the two summer scenarios. On the other hand,
there is a clear impact in the wing part of 183\,GHz for the two winter
scenarios. The same is true for 340\,GHz, but the influence of the surface
reflectivity is considerably lower. [* Comment somewhere on the implications of
this for retrievals at high latitudes *] Beside for the tropical case, for
229\,GHz there is a pronounced dependendency of the surface reflectivity, e.g.\
about 35\,K for mid-latitude winter.

\subsubsection{Clear-sky relative humidity weighting functions}
%
\dots

\subsubsection{Clear-sky transmissivities to space}
%
\dots

>>>>

[* Tbs, transmissivities and Jacobians are averaged over the channels *]

@@

\subsection{Overview of the 183, 229 and 325\,GHz bands}
%
The simulations in this section are based on five Fascod climate scenarios
(Sec.~\ref{sec:fascod}), and performed with a fixed sensor viewing angle of
25$^\circ$. No hydrometeors are included. For simpler interpretation of the
results, the reflectivity is set to have no frequency variation, i.e.\ the same
value is applied for all bands. The reflective is varied between 0 and 0.5.

In the figures covering transmissivities and Jacobians, ICI's 325\,GHz channels
are applied (Table~?).

\subsubsection{Clear-sky brightness temperatures}
%
Figure~\ref{fig:tb:r000} shows brightness temperatures over the three bands, for
a reflectivity of 0 (i.e.\ a blackbody surface). The figure takes into account
that the 183\,GHz channels of AWS are of single-sideband character, while for
229 and 325\,GHz averages of upper and lower sidebands are shown, plotted as
a function from the centre frequency on the lower side.

\begin{figure}[p]
  \centering
  \includegraphics[width=0.75\textwidth]{fascod_tb_r000}
  \caption{Solid lines show brightness temperatures for the lower wing of the
    183.31\,GHz transition. Dashed lines represent double-sideband measurements
    around 325.15\,GHz, with the mean of upper and lower band shown on the low
    side. Dash-dotted lines represent double-sideband measurements around
    229.00\,GHz in the same manner, but only over the bandwidth of the
    potential channel. For all three bands, spectra for all five
    Fascod scenarios are included.}
  \label{fig:tb:r000}
\end{figure}
\begin{figure}[p]
  \centering
  \includegraphics[width=0.75\textwidth]{fascod_tb_r050}
  \caption{Same as figure above, but with a surface reflectivity of 0.5.}
  \label{fig:tb:r050}
\end{figure}
\begin{figure}[p]
  \centering
  \includegraphics[width=0.75\textwidth]{fascod_tr_mls}
  \caption{Transmissivity to space as a function of altitude, for the
    mid-latitude summer scenario. Solid lines represent 183\,GHz channels,
    dashed lines 325\,GHz channels (ICI-5/6/7) and dashed-dotted the 229\,GHz
    channel. These transmissivities are independent of surface reflectivity.}
  \label{fig:tr:mls}
\end{figure}
\begin{figure}[p]
  \centering
  \includegraphics[width=0.75\textwidth]{fascod_wf_mls_025}
  \caption{Jacobians for relative humidity. Line symbols as in Fig.~\ref{fig:tr:mls}.
    Surface reflectivity is set to 0.25.}
  \label{fig:wf:mls:025}
\end{figure}

For 183 and 325\,GHz the brightness temperatures increase when moving away from
the centre frequency of the transition. The ``kinks'' in the spectra correspond
to ozone transitions, that are both more frequent and stronger in the 325\,GHz
range than in the 183\,GHz one. See Fig.~1 of \citet{eriksson:towar:20} for how
the ozone transitions are distributed between the lower and upper 325\,GHz
sideband. The spectra of 183 and 325\,GHz deviate little close to the transition
frequency, showing that the two frequencies are of similar strength, though the
325\,GHz one is slightly weaker. The higher deviations further out in the wings
are due to different contribution of far wing and continuum absorption, that is
higher at 325\,GHz. The 229\,GHz brightness temperatures is higher than any
value around 183 and 325\,GHz, as expected 229\,GHz being a window channel.

In Figure~\ref{fig:tb:r050} the surface reflectivity is changed to 0.5, which
should roughly correspond to the highest reflectivity encountered at these
frequencies. The differences to Fig.~\ref{fig:tb:r000}  are small for 183 and
325\,GHz for the tropical and the two summer scenarios. On the other hand,
there is a clear impact in the wing part of 183\,GHz for the two winter
scenarios. The same is true for 340\,GHz, but the influence of the surface
reflectivity is considerably lower. [* Comment somewhere on the implications of
this for retrievals at high latitudes *] Beside for the tropical case, for
229\,GHz there is a pronounced dependency of the surface reflectivity, e.g.\
about 35\,K for mid-latitude winter.

\subsubsection{Clear-sky transmissivities to space}
%
Assuming that a cloud layer can be moved in altitude, its impact on measured
brightness temperatures will roughly follow the transmissivity to space for the
cloud altitude. In short, where the transmissivity is zero the cloud will have
no impact, while where the transmissivity is unity the influence will be close
to constant with altitude (especially when the single scattering albedo is
high). This relationship just refers to the relative impact for a
given frequency, the absolute impact (at transmissivity 1) increases in general
with frequency.

Figure~\ref{fig:tr:mls} displays examples on transmissivities to space. The
transmissivities refers to the up-welling radiation. The contribution from
reflected down-welling is neglected and the considered transmissivity does not
depend on surface reflectivity.

The altitude variation of transmissivity exhibits same basic shape between all
the 183 and 325\,GHz channels, but the altitude of optical thickness of 1
(transmissivity of $e^{-1}\approx0.37$) varies. The curves of the end 183\,GHz
channels brackets the ones corresponding to the ICI 325\,GHZ channels. The later
channels show a higher deviation from 1 at 150\,hPa, due to some (weak) ozone
attenuation in the stratosphere. The 229\,GHz has the highest transmissivities.

\subsubsection{Clear-sky relative humidity weighting functions}
%
The sensitivity to humidity is most easily compared by the channels' weighting
functions (i.e.\ the Jacobian), and examples are found in
Fig.~\ref{fig:wf:mls:025}. The shape of the weighting functions depends on the
unity selected for representing water vapour. As the absolute amount of water
vapour varies with orders of magnitude from the surface to the tropopause, it
is difficult to interpret weighting functions for absolute humidity units and
it is more suitable to use a relative one. In Fig.~\ref{fig:wf:mls:025} the
weighting functions correspond to an increase of relative humidity (RH) with one
percent unit over 1\,km. RH with respect liquid/ice is applied above/below
0$^\circ$C.

The basic shape of the Jacobian is similar for all 183 and 325\,GHz channels,
but the peak altitude varies. The end 183\,GHz channels brackets the 325\,GHz
ICI ones, as for transmissivity. These Jacobians are negative, meaning that a
change towards higher humidity results in decreased brightness temperatures.
The 229\,GHz Jacobian is positive close to the surface, as this channel has
sensitivity all the way down to the surface and more water vapour just above a
reflecting surface results in higher brightness temperatures. The switch from
negative to positive Jacobian depends on atmospheric scenario and surface
reflectivity. For dry conditions also the outer 183 and 325\,GHz channels can
have a positive part, as long as the reflectivity is not close to 0.
